### 2014-01-01 VerboseNotes.tex
SU(2)などいろいろ追加
git-svn-id: https://dav.misho-web.com/svn/cyghome/trunk/QFT/CheatSheet@1044 c04c31ef-c4f7-4b37-ba94-86ebe2b9c820

%#!platexmake CheatSheet
%%% Time-Stamp: <>
%%% 一部で日本語が使用されています。

@@

>>>>

%#!platexmake CheatSheet
%%% Time-Stamp: <2014-01-02 02:19:22 misho>
%%% 一部で日本語が使用されています。

@@

\subparagraph{Conjugate representation}
Consider a representation $r$ and its generators $\{T_r^a\}$.
Then $\{-(T_r^a)^*\}$ also satisfies the group structure.
The corresponding representation is called the {\em conjugate representation} $\overline r$ of $r$:
\begin{equation}
 T_{\overline r}^a:=-(T_r^a)^*.
\end{equation}
If $\overline r$ is equivalent to $r$, i.e. there exists an unitary matrix $U$ such that
$T_{\overline r}^a=U^\dagger(T_r^a)U$, the representation $r$ is called a {\em real representation}.
This $U$ is unique up to a trivial scale factor, and either symmetric or anti-symmetric.
If $U$ is symmetric, the representation is called {\em real-positive}; otherwise {\em real-negative} or {\em pseudo-real}.

The $\boldsymbol2$ representation of $\gSU(2)$ is pseudo-real because
\begin{equation}
 T_{\overline {{\boldsymbol 2}}}^a \equiv -(\sigma^a/2)^* = \sigma^2(\sigma^a/2)\sigma^2.
\end{equation}

If a field $X$ transforms under a representation $r$, its complex conjugate does under $\overline r$:
\begin{equation}
  \delta X=\ii g\theta^a(T_r^a X)
\quad\Longrightarrow\quad
 \delta X^*
=-\ii g\theta^a(T_r^A X)^*
=\ii g\theta^a(T_{\overline r}^AX^*)
\end{equation}
